Audiovisual Analytics of social linked data

### 2017-11-13 latex/nuvem/nuvem1.tex
spell

\subsection{Critical theory and anthropological physics}\label{exp}
The potential for prejudice and the study of the self
were considered in~\cite{imp,stab,tese}.
In summary, the hubs, intermediary and periphery sectorialization
of a network might be achieved (or imposed) in a social network.
It yields a classification of the participants
by the comparison of the degree (or strength) distribution
against that of an Erdös-Rényi network.
Hubs are valued by literature
(although the intermediary are also reported as authorities
and structuraly most important agents)~\cite{ega},
which favors the potential for prejudice
of a quantitative classification (or typology)
of human beings.
At the same time, the classification of the participants
(hub, intermediary or peripheral)
vary in time constantly~\cite{stab,tese}
and across scales and networks,
which minimized the potential
for prejudice of such classification.

@@

The concept has reached other initiatives, such
as the Brazilian federal portal of social participation
ParticipaBR.
And have incited discussions that yield interesting concepts,
such as the fundamental cycle,
which is an idealized interaction between
Society and a management sector of it,
such as the State.
The individuals that feel the need to
change the way living is imposed by the State
should be able to act on the State,
have results and get paid for the time they put
into performing the social participation.
The existence of such a cycle would erradicate
extreme poverty, as the poor would be paid
to act and change State measures for the poor
or a community.
Thus, the ideal fundamental cycle is a social
participation model which is very shabbily practiced
and is defined by giving the one in need good conditions
to change the context which puts he/she in need.
The mechanisms or institutions that give the
individual the conditions and means to act
is then called the State or Government or,
more accurately nowadays, the Institutionalized Power.
Notice that, as such, the institutionalized power
have the goal to allow the interference 
of the individual in its management
and that this is extended to the private initiatives.
Social participation in the private sector
seems to be very incipient.

>>>>

\subsection{Critical theory and anthropological physics}\label{exp}
The potential for prejudice and the study of the self
were considered in~\cite{imp,stab,tese}.
In summary, the hubs, intermediary and periphery sectorialization
of a network might be achieved (or imposed) in a social network.
It yields a classification of the participants
by the comparison of the degree (or strength) distribution
against that of an Erdös-Rényi network.
Hubs are valued by literature
(although the intermediary are also reported as authorities
and structurally most important agents)~\cite{ega},
which favors the potential for prejudice
of a quantitative classification (or typology)
of human beings.
At the same time, the classification of the participants
(hub, intermediary or peripheral)
vary in time constantly~\cite{stab,tese}
and across scales and networks,
which minimized the potential
for prejudice of such classification.

@@

The concept has reached other initiatives, such
as the Brazilian federal portal of social participation
ParticipaBR.
And have incited discussions that yield interesting concepts,
such as the fundamental cycle,
which is an idealized interaction between
Society and a management sector of it,
such as the State.
The individuals that feel the need to
change the way living is imposed by the State
should be able to act on the State,
have results and get paid for the time they put
into performing the social participation.
The existence of such a cycle would eradicate
extreme poverty, as the poor would be paid
to act and change State measures for the poor
or a community.
Thus, the ideal fundamental cycle is a social
participation model which is very shabbily practiced
and is defined by giving the one in need good conditions
to change the context which puts he/she in need.
The mechanisms or institutions that give the
individual the conditions and means to act
is then called the State or Government or,
more accurately nowadays, the Institutionalized Power.
Notice that, as such, the institutionalized power
have the goal to allow the interference 
of the individual in its management
and that this is extended to the private initiatives.
Social participation in the private sector
seems to be very incipient.

### 2017-11-13 latex/nuvem/nuvem2.tex
spell

\begin{abstract}
	Audiovisual analytics of social data is useful for State and private
	management, scientific and individual endeavors.
	If there is data, information or knowledge in a computer,
	the observer or user should have it, the use of visual cues is an obvious,
	and sometimes considered optimized, strategy because of the efficiency and
	complexity of our visual cognition.
	Our sonic cognition is sometimes considered of greater complexity,
	due to patterns of music and spoken language.
	How to correctly formalize the mapping of data, information
	and knowledge to physical stimuli
	and then to the perceived stimuli
	respecting the Weber-Fechner and Steven's laws at least for visual
	and auditory cues?
\end{abstract}

>>>>

\begin{abstract}
	Audiovisual analytics of social data is useful for State and private
	management, scientific and individual endeavors.
	If there is data, information or knowledge in a computer,
	and the observer or user should have it, the employment of visual cues is an obvious,
	and sometimes considered optimized, strategy because of the efficiency and
	complexity of our visual cognition.
	Our sonic cognition is sometimes considered of greater complexity,
	due to patterns of music and spoken language.
	How to correctly formalize the mapping of data, information
	and knowledge to physical stimuli
	and then to the perceived stimuli
	respecting the Weber-Fechner and Steven's laws at least for visual
	and auditory cues?
\end{abstract}
